Parsing Postfix Log Files

### 2009-04-26 doc/logparser-implementation.tex
Changes based on comments from Ariane.

\showgraph{build/graph-number-of-action-invocations-excluding-22-and-62--68}{Number
of times each action was invoked when parsing \numberOFlogFILES{} log
files, excluding log files 22 \& 62--68}{Number of times each action was
invoked excluding 22 and 62--68}

@@

    \item [MAIL\_DISCARDED] Sometimes mail is discarded by Postfix, e.g.\
        mail submitted locally that is larger than the limit configured by
        the administrator.  This action is used for those mails; it invokes
        the \action{COMMIT} action, but is a separate action to simplify
        further analysis.

@@

    \item [MAIL\_TOO\_LARGE] When a client tries to send a mail larger than
        the local server accepts, the mail will be discarded by Postfix and
        the client informed of the problem.  The mail may have been
        accepted and partially transferred; if so the parser will have a
        data structure that must be disposed of.  See \sectionref{timeouts
        during data phase} for full details; although that describes
        timeouts, the processing is the same for mails that are too large.

@@

Rule conditions as part of the architecture have already been documented in
\sectionref{rule conditions in architecture}, and they can be very complex
and difficult to evaluate.  In contrast, \parsername{} uses quite simple
rule conditions: each rule has a \texttt{program} attribute that specifies
the Postfix component whose log lines it recognises, and each log line
contains the name of the Postfix component that produced it; when trying to
recognise log lines, the framework will only use rules where the two are
equal.  This avoids needlessly trying rules that will not recognise the log
line, or worse, might recognise it unintentionally.  In addition the
framework supports generic rules, whose program attribute is ``*''; these
will be used if none of the program-specific rules recognise the log line.
If none of the rules are successful the framework will warn the user,
informing them that they need to augment their ruleset, and alerting them
that the results stored in the database may be incomplete because
\parsername{} failed to recognise some log lines.

@@

    \item \parsername{} does not limit the size of the database, which will
        grow without bounds unless the user deletes connections and results
        from it.  This is both a limitation and a benefit: the benefit is
        that data will never be unexpectedly deleted, but the limitation is
        that the user must manage the size of the database.

>>>>

\showgraph{build/graph-number-of-action-invocations-excluding-22-and-62--68}{Number
of times each action was invoked when parsing \numberOFlogFILES{} log
files, excluding log files 22 \& 62--68 because their contents are
extremely skewed by mail loops}{Number of times each action was invoked
excluding 22 and 62--68}

\FloatBarrier{}

@@

    \item [MAIL\_DISCARDED] Sometimes mail is discarded by Postfix, e.g.\
        mail submitted locally on the server using \daemon{pickup} that is
        larger than the limit configured by the administrator.  This action
        is used for those mails; it invokes the \action{COMMIT} action, but
        is a separate action to simplify further analysis.

@@

    \item [MAIL\_TOO\_LARGE] When a remote client tries to send a mail over
        \acronym{SMTP} that is larger than the server accepts, the mail
        will be discarded by Postfix and the client informed of the
        problem.  The mail may have been accepted and partially
        transferred; if so the parser will have a data structure that must
        be disposed of.  See \sectionref{timeouts during data phase} for
        full details; although that describes timeouts, the processing is
        the same for mails that are too large.

@@

Rule conditions as part of the architecture have already been documented in
\sectionref{rule conditions in architecture}, and they can be very complex
and difficult to evaluate.  Complex conditions are not required in parsers
based on this architecture: \parsername{} uses quite simple
rule conditions.  Each rule has a \texttt{program} attribute that specifies
the Postfix component whose log lines it recognises, and each log line
contains the name of the Postfix component that produced it; when trying to
recognise log lines, the framework will only use rules where the two are
equal.  This avoids needlessly trying rules that will not recognise the log
line, or worse, might recognise it unintentionally.  In addition the
framework supports generic rules, whose program attribute is ``*''; these
will be used if none of the program-specific rules recognise the log line.
If none of the rules are successful the framework will warn the user,
informing them that they need to augment their ruleset, and alerting them
that the results stored in the database may be incomplete because
\parsername{} failed to recognise some log lines.

@@

    \item \parsername{} does not limit the size of the database, which will
        grow without bounds unless the user deletes connections and results
        from it.  This is both a benefit and a limitation: the benefit is
        that data will never be unexpectedly deleted, but the limitation is
        that the user must manage the size of the database.

### 2009-04-26 doc/logparser-results.tex
Changes based on proofreading chapters 4 and 5.
Changes based on comments from Ariane.

@@

@@

@@

        Optimal ordering reduces parsing time by
        \input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
        relative to shuffled ordering; actions occupy
        \input{build/include-percentage-time-spent-processing-log-lines-mean}
        of parsing time, less if any optimisations are disabled, so
        optimising actions could not possibly provide as big a performance
        increase as optimally ordering rules.  Similarly, caching compiled
        regexes provides an
        \input{build/include-cached-regexes-vs-discarded-regexes-mean-reduction}
        reduction in parsing time; not invoking actions at all reduces the
        most optimised parsing time by less than half that.  If processing
        of recognised log lines was optimised to 1\% of its original
        parsing time, it would be only slightly more effective than optimal
        ordering, but it would be vastly harder to implement; optimising
        actions would not reduce parsing time enough to justify the amount
        of effort required.

>>>>

The standard deviation for mails received on weekend days is
quite high, because approximately four times the usual number of mails was
received on the weekend contained in the $16^{th}$ and $17^{th}$ log files.
The standard deviation for all days is high because the high number of
mails received during log files 16, 17, 35, 36, 39, and 40.  Interestingly,
the extra mail received during log files 35, 36, 39, and 40 stopped during
log files 37 and 38, which may indicate that it was a virus infected office
machine that was turned off over the weekend.  Unfortunately, the source
cannot be investigated properly because all the mails in question were
relayed via the department's secondary MX (a backup mail server, hosted
elsewhere), so the log files showing the original source were unavailable.

@@

\label{Characteristics of the 93 log files}

@@

XXX TAKE UP SOME SPACE\@.

XXX TAKE UP SOME SPACE\@.

XXX TAKE UP SOME SPACE\@.

@@

        Optimal ordering reduces parsing time by
        \input{build/include-optimal-ordering-parsing-time-reduction-other-logs}\%
        relative to shuffled ordering; actions occupy
        \input{build/include-percentage-time-spent-processing-log-lines-mean}
        of parsing time, less if any optimisations are disabled, so
        optimising actions could not possibly provide as big a performance
        increase as optimally ordering rules.  Similarly, caching compiled
        regexes provides an
        \input{build/include-cached-regexes-vs-discarded-regexes-mean-reduction}
        reduction in parsing time; not invoking actions at all reduces the
        most optimised parsing time by less than half that.  If processing
        of recognised log lines was optimised to 1\% of its original
        parsing time, it would be only slightly more effective than optimal
        ordering, but it would be vastly more difficult to implement;
        optimising actions would not reduce parsing time enough to justify
        the amount of effort required.
